Controlled growth and property measurement of one-dimensional oxide nanostructures for energy applications

### 2015-03-09 misc/SI_thesis.tex
update on mwe files

@@

@@

@@

\ce{WS2} hydrogen evolution,\cite{Voiry2013a}

@@

>>>>

self-nucleation from vapor of new crystals, new liquid drops and 2D monolayers on a saturated crystal face requires supersaturations of the vapor by factors of 10, 5, and 1.5 respectively; the presence of dislocation, however, breaks the need for fresh 2D nucleation. perfect metal exhibits 1E+8 dislocation lines each square centimeter.\cite{Frank1949}

solid-solid wetting for \ce{MoO3}, \ce{WO3}, and \ce{V2O5} spreading.\cite{Leyrer1988} Experimental evidence supports the oxyhydroxide are intermediates in the surface chemical transformation of these oxides into surface polyoxoanions in the presence of \ce{H2O} vapor. The spreading occurs independent of polymolybdate formation and in the absence of \ce{H2O} vapor; the solid-solid wetting driven by a gradient of the surface free energy. Gas form transport is discarded as the dominanting mechanism.

\ce{MoO3} wet \ce{Al2O3} and \ce{TiO2} but not \ce{SiO2}; \ce{MoO3} reacts with \ce{Al2O3} in solid state to form \ce{Al2(MoO4)3} and with \ce{TiO2} to form \ce{Ti(MoO4)2}, yet reaction with \ce{SiO2} not reported.

1D review. show more exotic phenomena, spin-charge separation. Au-Si NW growth terminate as Au, not a Au-Si alloy.\cite{Hu1999}

an order-of-magnitude estimate, to a lesser extent,

@@

Basic operations and several growth recipes using the home-built cvd system are included in Appendix.

the TEM specimen was prepared either by directly scratching the as-synthesized sample using TEM grid (Cu, lacy carbon, 300 mesh), or dispersed into aqueous or organic solutions, then drop-cast onto TEM grid.

The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013}

It is well known that in lamellar flow region, there is a velocity boundary above the side wall.

Raman band assignment for \ce{A2MO4} is well grounded. Alkali metal cations with octahedral coordination occur below 230 cm$^{-1}$. For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.

Based on the vls process, it is known that a eutectic state is the key to promote preferred growth direction
The melting of \ce{Na2MoO4} was highly possible when taking into account of its size as well.\cite{Bruggemann1997}

\begin{itemize}

\item When no Mo powder was used while growth was performed in an old tube or oxygen flow is limited to a extreme small value, circular particle-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism. Using Mo coated substrate and subsequent NaOH treatment, similar particles formation was repeated. No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
\item 30 min growth: belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu$ m/s), tower structures show up as well, but much less than belt. Two kinds of belts found, tapering and non-tapering. The former one seems to have particles mostly associated with sidewalls of the top part.
\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip. XRD pattern indicated the existence of \ce{Na_xMoO3} phase. And \ce{MoO3} XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
\item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one particle located along the interface of two perpendicular belts, EDX confirmed high Na content.

\end{itemize}

people used chamber pot when there was no running water system. 
This difference presumably vanished when nanotube diameter exceeded 100 nm. considering the integration into current microelectronic process, which was found higher for film prepared without an intermediate Ni coating

This thesis then conjectured that the substrate cleaning in Ref.\cite{Peimyoo2013} should be similar to that in Ref.\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure were still needed to be optimized with respect to the home-built CVD apparatus. No 1L vs nL statistic is available.

15 optical modes e allowed assuming 6 atoms in primitive cell.

@@

\ce{WS2} exciton binding energy 0.71 eV , exciton A of 2 eV and B of 2.4 eV from direct band gap at K valley of the BZ. \cite{Zhu2014a}

photocarrier relaxation pathway in TMDC by Monte-Carlo simulation.\cite{Kozawa2014} the excitation at K point, the path way and radiative emission channels are related to band nesting.

Substrate effects on Raman and PL of TMDC.\cite{Buscema2014} \ce{MoS2} PL on Au is not quenched for 1L.

Si work function, 4.83 eV throughout most of the doping range.\cite{Allen1962} be open to reinterpretation; work function $\psi$ is determined using the Kelvin contact potential difference method against a metal reference. $\psi_m$ is determined by a photoelectric measurement.

1T \ce{WS2} hydrogen evolution.\cite{Voiry2013a}

\ce{WS2} nanotube has been studied because of the strong lubricant;  
The sulfurization of tungsten oxide, proved as a high yield approach, has been studied throughly for preparing \ce{WS2} nanotubes. Few wall \ce{WS2} can be used to obtain nanoribbon. The properties of \ce{WS2} nanotube can help to understand the confinement in \ce{WS2} nanoribbon.

The growth design, emphasizing the absence of \ce{H2};

@@

\ce{WS2} hydrogen evolution can be achieved by using large potential and expensive Pt-based catalysts. Finding inexpensive replacement would enable large scale HER applications.\cite{Voiry2013a} \ce{WS2} nanosheets exfoliated by chemical reaction, and 1T (octahedral) phase is associated with the enhanced electrocatalytic activity. Energy barrier from 1T to 2H transformation is calculated to be 0.95 eV, explained why 1T is stable in ambient environment.

aqueous suspension, de-aerated with Ar.

TCO band alignment.\cite{Klein2010} The energy band alignment between TCO and organic materials is governed by vacuum level to a large extent; whereas the alignment with inorganic materials is modfied by the interficial dipole significantly.

Work function (minus of the Fermi level wrt vacuum) of two contributions: electrical work for passing the intrinsic surface dipole layer and the other one is equivalent to the chemical potential $\mu$ of the electrons in the bulk material, measured with respect to the vacuum in absence of a dipole layer on the surface.\cite{Gerischer1983} Different crystallographic orientation surfaces have different dipoles. The Fermi level position relative to the vacuum level therefore depends on the surface structure.

Charge separation and the geometrical influence. catalytic activity is associated to the oxygen vacancy, substoichiometry, or plasmon. \ce{WO3} nanosheet carrier density derived from UV-Vis using Drude model $\omega_p = \sqrt{\frac{N_e e^2}{\epsilon_0 m_e}}$ and from Mott-Schottky measurement. PL data of \ce{WO3-x} obtained using 360 nm excitation.\cite{Yan2015}

\ce{MoS2} FET.\cite{Li2015}

(Good writing) Hot carriers generation and collection device bansed on TCO.\cite{Gong2014a} Metal-SC contact as Schottky photodetector, where hot electron generated in metal and was injected into SC. ITO-\ce{Al2O3}-Au, where e in Au traverse 5 nm \ce{Al2O3}.

alternatively, hot electrons, carrier cooling, losing kinetics energy to lattice, phonon emission.

@@

How the large exciton binding energy affect the optical properties in TMDC. out-of-plane acoustic (ZA), \cite{Zhang2015tmdc}

In ambient environment, \ce{MoS2} oxidized into oxides when $T > 350$ \si{\degreeCelsius}.\cite{Su2014a}

For Raman, the total scattered intensity $I(\lambda)$ is 
\[
I(\lambda) = \int_0^d |F_{abs}(\lambda_0,x)\cdot F_{sc}(\lambda, x)|dx
\]
where $F_{abs}$ can be found in the ESI of ref.\cite{Buscema2014}. The enhancement factor is hereby defined as the ratio of intensity between free standing layer and substrate-specfic layer.

Raman and PL of \ce{MoS2} on dielectric and conducting substrates. 514 nm, 20 $\mu$m aperture, 0.5 \si{cm^{-1}} resolution, 0.25 mW power, and 10 s integration time. \cite{Buscema2014} The substrate-dependent interferometric stacking does not perturb the peak emission wavelength but strongly influences the emission intensity. \ce{SiO2} charge impurity induced doping, leading to enhanced electron density, is proposed to explain the softening of A1g mode on \ce{SiO2}.

metallic sub affect PL by additional non-radiative path for exciton recombination, such as charge transfer and dipole-dipole interaction. But on Au \ce{MoS2} PL is enhanced compared to that on \ce{SiO2} after normalization. Charged exciton results in PL in redshifted wavelength.

### 2015-03-09 misc/paper.tex
update on mwe files

In energy band structure of $E-k$, the zero energy is chosen at the top of VB, so the $E$ here should be chemical potential, \cite{Sze2006} 
When defining the Fermi level, the follow integral is used
\[
n = \int_{E_C}^\infty N(E)f(E)dE
\]
So the Fermi level is again compared to the VBM.

@@

Basic operations and several growth recipes using the home-built \gls{cvd} system are included in Appendix.

the TEM specimen was prepared either by directly scratching the as-synthesized sample using TEM grid (Cu, lacy carbon, 300 mesh), or dispersed into aqueous or organic solutions, then drop-cast onto TEM grid.

The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013}

It is well known that in lamellar flow region, there is a velocity boundary above the side wall.

Raman band assignment for \ce{A2MO4} is well grounded. Alkali metal cations with octahedral coordination occur below 230 cm$^{-1}$. For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.

Based on the \gls{vls} process, it is known that a eutectic state is the key to promote preferred growth direction
The melting of \ce{Na2MoO4} was highly possible when taking into account of its size as well.\cite{Bruggemann1997}

\item When no Mo powder was used while growth was performed in an old tube or oxygen flow is limited to a extreme small value, circular particle-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism. Using Mo coated substrate and subsequent NaOH treatment, similar particles formation was repeated. No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
\item 30 min growth: belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu$ m/s), tower structures show up as well, but much less than belt. Two kinds of belts found, tapering and non-tapering. The former one seems to have particles mostly associated with sidewalls of the top part.
\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip. XRD pattern indicated the existence of \ce{Na_xMoO3} phase. And \ce{MoO3} XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
\item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one particle located along the interface of two perpendicular belts, EDX confirmed high Na content.

people used chamber pot when there was no running water system. 
This difference presumably vanished when nanotube diameter exceeded 100 nm. considering the integration into current microelectronic process, which was found higher for film prepared without an intermediate Ni coating

This thesis then conjectured that the substrate cleaning in Ref.\cite{Peimyoo2013} should be similar to that in Ref.\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure were still needed to be optimized with respect to the home-built CVD apparatus. No 1L vs nL statistic is available.

15 optical modes e allowed assuming 6 atoms in primitive cell.

>>>>

@@

\section{sze ssp}
\subsection{review of semiconductor}
zincblende structure: two interpenetrating fcc lattices; wurtzite structure: two interpenetrating hexagonal lattices. band structure, that is energy-momentum relationship, is usually obtained by solving the Schrodinger equations in one electron approximation.

In energy band structure of $E-k$, the zero energy is chosen at the top of VB, so the $E$ here should be chemical potential.\cite{Sze2006} The electron energy is conventionally defined to be positive when measured upward from $E_c$; the hole energy is positive when measured downward from $E_v$. When defining the Fermi level, the follow integral is used
\[
n = \int_{E_C}^\infty N(E)f(E)dE
\]
So the Fermi level is again compared to the VBM. DOS $N(E)$ is approximated by the density near the bottom of conduction band;

\subsection{metal-SC contacts}

Schottky suggested that potential barrier could arise from stable space charges alone.

contact potential means the potential difference between the work functions.

Covalent SC surface has high peak density of surface states, and the neutral level is about one-third of the bandgap from valence-band edge. ForIII-V compounds, the pinning of surface Fermi level occurs, leading to the barrier height independent of metal work function,

For ionic SC, the barrier height depends strongly on the metal.
